---
title: "Tooltip Display in Tracks"
---

Tooltip can be specified by supplying a data frame when constructing the track
and it can be modified after the track is constructed.

By default, when constructing a track from GRanges/IRanges, the tooltip is converted
from the "meta-columns" of GRanges/IRanges, i.e. `mcols(d)`.


```{r}
suppressPackageStartupMessages({
    library(TnT)
    library(GenomicFeatures)
    library(TxDb.Hsapiens.UCSC.hg19.knownGene)
    library(org.Hs.eg.db)
})
txdb <- TxDb.Hsapiens.UCSC.hg19.knownGene
```


## Basic Example using BlockTrack

Click on the block to see the tooltip.

```{r}
myIRanges <- IRanges(c(10, 100, 1000), width = c(30, 50, 500))
mytooltip <- as.data.frame(myIRanges)
myTrack <- TnT::BlockTrack(myIRanges, tooltip = mytooltip)
#TnTBoard(myTrack, IRanges(1, 2000))
TnTBoard(myTrack, GRanges("UnKnown", IRanges(1, 2000)))
```

<br/> <br/>

## Modify Tooltip of a Constructed Track

First, construct a gene track from the TxDb object.

```{r}
geneTrack <- TnT::GeneTrackFromTxDb(txdb, height = 300)
```

We can extract and replace the tooltip with `tooltip` and `tooltip<-`.
In this case, we use the organism database to find the corresponding gene names of
every gene, then add them to the tooltip.

```{r}
head(df.tooltip <- TnT::tooltip(geneTrack))

genename <- AnnotationDbi::select(org.Hs.eg.db, as.character(df.tooltip$gene_id),
                      columns = "SYMBOL", keytype = "ENTREZID")
df.tooltip$gene_symbol <- genename$SYMBOL[match(df.tooltip$gene_id, genename$ENTREZID)]
TnT::tooltip(geneTrack) <- df.tooltip
head(TnT::tooltip(geneTrack))
```

We can also modify the label to show gene symbol instead of entrez ID.

```{r}
geneTrack$display_label <- TnT::strandlabel(TnT::tooltip(geneTrack)$gene_symbol,
                                            strand(TnT::trackData(geneTrack)))
```

Click to see the tooltip.

```{r}
TnTGenome(geneTrack, GRanges("chrX", IRanges(100000, 10000000)))
```

<br/> <br/>


## Use Sub-headers in Tooltip

Columns of empty strings will be regarded as subsection titles, for example:

```{r}
head(df.tooltip)
df.tooltip <- cbind(
    data.frame(`Identity` = ""),
    df.tooltip[c("gene_id", "gene_symbol")]
)
```

Click to see.

```{r}
TnT::tooltip(geneTrack) <- df.tooltip
TnTGenome(geneTrack, GRanges("chrX", IRanges(100000, 10000000)))
```

<br/> <br/>


## Session Info

```{r}
sessionInfo()
```

