---
title: "TnT Examples"
---

This page contains examples of visualization created with TnT package.

```{r, include=FALSE}
suppressPackageStartupMessages({
    library(TnT)
    library(GenomicFeatures)
})
```

------

## TnT Board and TnT Genome


------

## Different Track Types and Their Constructors

### [Block Track](tracktype-BlockTrack.html)

```{r, echo=FALSE}
ir <- IRanges(c(100, 400, 800), width = c(100, 150, 250))
gr <- GRanges("na", ir)
bt <- BlockTrack(gr, color = "salmon2", label = NULL)
TnTBoard(bt, view.range = range(gr) * .7, coord.range = ranges(range(gr)) * .5)
```

<br> </br>

### [Pin Track](tracktype-PinTrack.html)

```{r, echo=FALSE}
ir <- IRanges(start = c(100, 200, 300, 400), width = 1)
gpos <- GRanges("na", ir)
gpos$value <- 1:4

ptrack <- PinTrack(gpos, color = c("green", "blue", "yellow", "red"), label = NULL)
TnTBoard(ptrack, view.range = GRanges("na", IRanges(0, 500)), coord.range = IRanges(0, 500))
```

<br> </br>

### [Line Track and Area Track](tracktype-LineTrack-AreaTrack.html)

```{r, echo=FALSE}
pos <- IRanges(seq(0, 500, by = 10), width = 1)
pos <- GRanges("na", pos)
pos$value <- c(1, 0.6, 0.1, 0.7, 0.1, 0, 0.9, 0.4, 0.6, 0.1, 0, 0.8, 0.4,  0.5, 0.3, 0.2, 0.3, 0.8, 0.1, 0.8, 0.1, 0, 1, 0.3, 0, 0.9, 1,  0.6, 0.6, 0.1, 0.9, 0.3, 0.7, 0.2, 0.2, 0.6, 0.1, 0, 1, 0.6,  0.1, 0.5, 0.2, 0.4, 0, 1, 0, 0.4, 0.6, 0.5, 0)
lt <- LineTrack(pos, domain = c(0, 1), label = NULL, color = "steelblue", height = 40)
at <- AreaTrack(pos, domain = c(0, 1), label = NULL, color = "orange", height = 40)
TnTBoard(c(lt, at), view.range = GRanges("na", IRanges(0, 500)), coord.range = IRanges(0, 500),
         zoom.allow = IRanges(70, 500))
```

<br> </br>

### [Vline Track](tracktype-VlineTrack.html)

```{r, echo=FALSE}
```

<br> </br>

### [Gene Track and Feature Track](tracktype-GeneTrack.html)

```{r, echo=FALSE}
suppressPackageStartupMessages(library(EnsDb.Hsapiens.v86))
gene <- genes(EnsDb.Hsapiens.v86)
genetrack <- FeatureTrack(gene, tooltip = as.data.frame(gene), height = 100, color = "darkslategray4")
TnTGenome(genetrack, view.range = gene[gene$symbol == "BRCA2"][1] * .5)
```

<br> </br>

### [Tx Track and FeatureGroup Track](tracktype-TxTrack.html)

```{r, echo=FALSE}
```

<br> </br>


### [Composite Track](track-CompositeTrack.html)

```{r, echo=FALSE}
```

<br> </br>

------

## Track Manipulation

### [Background, Height and Label (`trackSpec` and `trackSpec<-`)]()

### [Track Data (`trackData` and `trackData<-`)]()

------

## Tooltip

### [Tooltip display for tracks](track-tooltip-display.html)

------

## Colors

### [Feature colors](track-colors.html)


```{r, echo=FALSE}
suppressMessages({
    library(TnT)
    library(EnsDb.Hsapiens.v86)
    gene <- genes(EnsDb.Hsapiens.v86)
    genetrack <- FeatureTrack(gene, tooltip = as.data.frame(gene), height = 100,
                              color = mapcol(gene$gene_biotype, palette.fun = grDevices::rainbow))
    TnTGenome(genetrack, view.range = gene[gene$symbol == "BRCA2"][1] * .5)
})
```



------

## Low level utils

### [trackWidget](trackWidget.html)

------

