---
title: "Composite Track"
---

Composite track is a way to combine multiple types of features into one track.
A composite track can be constructed by combining a list of different tracks with function `merge`.

Label, background and height of the composite track will be derived from the component tracks and
can be further accessed and modified with `trackSpec` and `trackSpec<-`.


```{r}
suppressPackageStartupMessages({
    library(TnT)
    library(GenomicFeatures)
    library(AnnotationHub)
})
set.seed(42)
```


## Composite a Block Track and a Pin Track

First to construct a block track and a pin track from data.

```{r}
gr <- GRanges("chr1", IRanges(c(11000, 20000, 60000), width = 2000))
gpos <- GRanges("chr1", IRanges(c(12000, 21000, 61000), width = 1), value = c(1, 2, 3))

btrack <- BlockTrack(gr, label = "Block Track", tooltip = as.data.frame(gr), color = "lightblue4")
ptrack <- PinTrack(gpos, label = "Pin Track", tooltip = as.data.frame(gpos), background = "beige")
```

Then use `merge` to construct a composite track and showing it.

```{r}
ctrack <- merge(btrack, ptrack)
TnTBoard(ctrack)
```

<br/> <br/>

Be aware that the components in a composite track are rendered according to the order
in `merge`. For example, the block track will cover the pin track if we switch the order.

```{r}
TnTBoard(merge(ptrack, btrack)) # the pin track has been covered
```

<br/> <br/>

Show all three tracks and add axis indicator.

```{r}
TnTGenome(list(ctrack, ptrack, btrack))
```


<br/> <br/>


## Gene Track and CpG Islands

```{r}
library(TxDb.Hsapiens.UCSC.hg19.knownGene)
txdb <- TxDb.Hsapiens.UCSC.hg19.knownGene
gtrack <- GeneTrack(txdb, label = "Gene", color = "burlywood3")

ah <- AnnotationHub()
ah <- query(ah, "cpgisland")
cpg <- ah[[names(ah[ah$genome == "hg19"])]]
cpgtrack <- BlockTrack(cpg, label = "CpG Islands", tooltip = as.data.frame(cpg),
                       color = "lightblue")
TnTGenome(merge(cpgtrack, gtrack), view.range = GRanges("chr1", IRanges(84884317, 85205497)))
```

<br/> <br/>



## Session Info

```{r}
sessionInfo()
```
