---
title: "Colors of Track"
---

Colors of features in a track can be specified with a character vector which will
be expanded to the same length of track data. The values will be part of the track
data and can be modified after the track is constructed.


```{r}
suppressPackageStartupMessages({
    library(TnT)
    library(GenomicFeatures)
    library(magrittr)
})
```


## R Color Names

This example shows all available color names in R with a block track.


```{r}
colors <- colors()
data <- GRanges("Unknown", IRanges(seq_along(colors), width = 2), "Color Name" = colors)
track <- BlockTrack(data, color = data$"Color Name", label = NULL)
TnTBoard(track)
```

<br/> <br/>

## Use Color Palettes

R have functions to assist the picking of colors, by which a qualitative value
can be mapped to colors, e.g. the `rainbow` function.

```{r}
# A helper function
showCols <- function (colors) {
    data <- GRanges("Unknown", IRanges(seq_along(colors), width = 2), "Color" = colors)
    track <- BlockTrack(data, color = data$"Color", label = NULL)
    TnTBoard(track, view.range = range(data))
}
showCols(rainbow(6))
showCols(heat.colors(6))
showCols(terrain.colors(6))
showCols(topo.colors(6))
showCols(cm.colors(6))
```


## Session Info

```{r}
sessionInfo()
```

